A meta-analysis of mental rotation ability in the first years of life

### 2022-04-26 code/analysis.Rmd
Order experiments by year
Add study table

# Directory paths
data_dir <- here("data")
figures_dir <- here("results/figures")

@@

    # Add unique experiment identifier
    experiment = str_c(article, group, seq = ", "),

@@

    # Compute empirical correlation based on sd_z and condition SDs
    d_z = case_when(
      !is.na(d_z_t) ~ d_z_t,
      !is.na(d_z_f) ~ d_z_f,
      !is.na(d_z_diff) ~ d_z_diff
    ),
    sd_z = mean_diff / d_z,
    ri = (sd_z^2 - sd_novel^2 - sd_familiar^2) / (-2 * sd_novel * sd_familiar)
  ) -> dat_all

@@

# Compute standard error of Cohen's d based on assumed correlation
# See Hedges' formula on p. 253 in http://dx.doi.org/10.20982/tqmp.14.4.p242
# This will need a sensitivity analysis regarding the values of `r_assumed`
r_assumed <- 0.5
dat_all %>%
  mutate(
    ni = sample_size,
    vi = (dfi / (dfi - 2)) * ((2 * (1 - r_assumed)) / ni) *
      (1 + gi^2 * (ni / (2 * (1 - r_assumed)))) - (gi^2 / ji^2),
    sei = sqrt(vi)
  ) %>%
  filter(!is.na(gi)) %>%
  select(
    article,
    group,
    group_long,
    experiment,
    gender_split,
    gi,
    ni,
    vi,
    sei,
    female_percent,
    age_mean,
    age_sd,
    age_min,
    age_max,
    task
  ) -> dat_all_r

@@

# Helper functions for printing confidence intervals
print_num <- function(x) format(round(x, 2), trim = TRUE, nsmall = 2)
print_ci <- function(est, lb, ub) {
  paste0(print_num(est), " [", print_num(lb), ", ", print_num(ub), "]")
}

@@

>>>>

# Directory paths
data_dir <- here("data")
figures_dir <- here("results/figures")
tables_dir <- here("results/tables")

@@

    # Add unique experiment identifier
    experiment = str_c(year, article, group, seq = ", "),

@@

    # Compute empirical correlation based on sd_z and condition SDs
    d_z = case_when(
      !is.na(d_z_t) ~ d_z_t,
      !is.na(d_z_f) ~ d_z_f,
      !is.na(d_z_diff) ~ d_z_diff
    ),
    sd_z = mean_diff / d_z,
    ri = (sd_z^2 - sd_novel^2 - sd_familiar^2) / (-2 * sd_novel * sd_familiar)
  ) %>%
  # Order rows by experiment ID
  arrange(experiment) -> dat_all

@@

# Compute standard error of Cohen's d based on assumed correlation
# See Hedges' formula on p. 253 in http://dx.doi.org/10.20982/tqmp.14.4.p242
# This will need a sensitivity analysis regarding the values of `r_assumed`
r_assumed <- 0.5
dat_all %>%
  mutate(
    ni = sample_size,
    vi = (dfi / (dfi - 2)) * ((2 * (1 - r_assumed)) / ni) *
      (1 + gi^2 * (ni / (2 * (1 - r_assumed)))) - (gi^2 / ji^2),
    sei = sqrt(vi)
  ) %>%
  filter(!is.na(gi)) -> dat_all_r

@@

# Helper functions for printing confidence intervals
print_num <- function(x, digits = 2) {
  x <- format(round(x, digits), trim = TRUE, nsmall = digits)
  x[x == "NA"] <- NA
  return(x)
}
print_ci <- function(est, lb, ub) {
  paste0(print_num(est), " [", print_num(lb), ", ", print_num(ub), "]")
}

@@

```{r, tab_within}
# Helper functions to re-format age in years and/or months
format_days_years <- function(days) {
  days_per_year <- 365.25
  days_per_month <- 30.417
  years <- days %/% days_per_year
  months <- round((days - years * days_per_year) / days_per_month)
  str <- paste0(as.character(years), "y ", as.character(months), "m")
  str[is.na(days)] <- NA
  return(str)
}
format_days_months <- function(days, digits = 1) {
  days_per_month <- 30.417
  months <- days / days_per_month
  str <- format(round(months, digits), trim = TRUE, nsmall = digits)
  str <- paste0(str, "m")
  str[is.na(days)] <- NA
  return(str)
}

# Save within-analysis table of experiments
dat %>%
  transmute(
    Article = if_else(article == lag(article, default = ""), "", article),
    Experiment = group_long,
    `Sample size` = sample_size,
    `Females` = round(female_percent * sample_size),
    `Mean age^a` = format_days_years(age_mean),
    SD = format_days_months(age_sd),
    Task = task,
    `Stimulus type` = str_to_sentence(stimuli_presentation),
    `Stimulus dimensions` = stimuli_dimensions
  ) %>%
  print(n = Inf)
write_csv(
  file = here(tables_dir, "within_experiments.csv"),
  na = "n/a"
)
```
